Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-01 R0V0.tex
Merge Ian's changes regarding the distributed design

\section{Distributed Design of Distributed Controllers}

@@

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.

>>>>

\section{Distributed Design of Distributed Controllers}\label{sec:distributed_design}

@@

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.

\mypara Further conditions are discussed in \cite{manchester_existence_2018}.
